### 2008-12-20 talk/ecoop2009/conclusion.tex
put two code snippets side by side, and fix a typo
try to write the related work section in proper english

\section{Related Word}
Promotion is a concept that we have already explored in other contexts. Psyco is
a run-time specialiser for Python that uses promotion (called ``unlift'' in
\cite{DBLP:conf/pepm/Rigo04}). However, Psyco is a manually written JIT, is
not applicable to other languages and cannot be retargetted.

 - reference standard jit stuff, PICs \cite{hoelzle_optimizing_1991}, this one: http://www.cs.ucsb.edu/~urs/oocsb/self/papers/type-feedback.html

 - compare against tracing JITs \cite{gal_hotpathvm_2006}. tracing jits make
 implementing jits much easier, maybe less need for JIT generation. also, they
 concentrate on loops, which makes them produce a lot less code (which will need
 to be addressed in our work as well).

 so far tracing JITs have less general allocation removal techniques, which
 makes them get less speedup in a dynamic language with boxing

in my master I had this snippet:

"""
The generated code typically contains guards; in recent research
\cite{gal_incremental_2006} on Java, these guards' behaviour is extended to be
similar to our promotion.  This has been used twice to implement a dynamic
language (JavaScript), by Tamarin\footnote{{\tt
http://www.mozilla.org/projects/tamarin/}} and in \cite{chang_efficient_2007}.
"""

@@

 - apart from that we maybe should talk about escape analysis
 \cite{Blanchet99escapeanalysis}, \cite{Choi99escapeanalysis}
 our algorithm is totally simple-minded in comparison, but is useful in practise

>>>>

\section{Related Work}

Promotion is a concept that we have already explored in other contexts. Psyco is
a run-time specialiser for Python that uses promotion (called ``unlift'' in
\cite{DBLP:conf/pepm/Rigo04}). However, Psyco is a manually written JIT, is
not applicable to other languages and cannot be retargetted.

Moreover, the idea of promotion of is a generalization of \emph{Polymorphic
  Inline Caches} \cite{hoelzle_optimizing_1991}, as well as the idea of using
runtime feedback to produce more efficient code
\cite{hoelzle_type_feedback_1994}.

PyPy-style JIT compilers are hard to write manually, thus we chose to write a
JIT generator.  Tracing JIT compilers \cite{gal_hotpathvm_2006} also gives
good results but are much easier to write, making the need for an automatic
generator less urgent.  However so far tracing JITs have less general
allocation removal techniques, which makes them get less speedup in a dynamic
language with boxing.  Another difference is that tracing JITs concentrate on
loops, which makes them produce a lot less code.  This issue will be addressed
by future research in PyPy.

The code generated by tracing JITs code typically contains guards; in recent research
\cite{gal_incremental_2006} on Java, these guards' behaviour is extended to be
similar to our promotion.  This has been used twice to implement a dynamic
language (JavaScript), by Tamarin\footnote{{\tt
http://www.mozilla.org/projects/tamarin/}} and in \cite{chang_efficient_2007}.

@@

Our algorithm to avoid allocation of unneeded intermediate objects fits into
the research area of escape analysis: in comparison to advanced techniques
\cite{Blanchet99escapeanalysis}, \cite{Choi99escapeanalysis} our algorithm is
totally simple-minded, but it is still useful in practise.
